Analyzing Network Transfer Protocols on a Simulated Interplanetary Internet

### 2024-04-10 paper/paper.tex
add missing citations

The first assumption made was that all orbits are circular. Realistically,
orbits are oval shaped, with the two focal points. A result of this assumption
is the elimination of any difference in orbital speed due to Kepler's third law.
The orbital radius was chosen by taking the average orbital radius of the real
life celestial bodies. For example Earth's average orbital radius is 149.6
billion meters~\cite{}, and therefore orbits around the sun in a circular orbit
of radius 149.6 billion meters. Another result of this assumption is that orbits
are considered to be centered around the body which it orbits. The Mars orbit
has a focal point that is further in space, making it more oval shaped than the
earth orbit.~\cite{} While this could make changes to a simulated network in
some very specific situations, the primary behaviour of a solar system is
maintained, like retrograde orbits, periodical alignment, predictable behaviour,
and recursive orbits of sub orbiting object.

>>>>

The first assumption made was that all orbits are circular. Realistically,
orbits are oval shaped, with the two focal points. A result of this assumption
is the elimination of any difference in orbital speed due to Kepler's third law.
The orbital radius was chosen by taking the average orbital radius of the real
life celestial bodies. For example Earth's average orbital radius is 149.6
billion meters~\cite{nasa_earth}, and therefore orbits around the sun in a
circular orbit of radius 149.6 billion meters. Another result of this assumption
is that orbits are considered to be centered around the body which it orbits.
The Mars orbit has a focal point that is further in space, making it more oval
shaped than the earth orbit.~\cite{nasa_mars} While this could make changes to a
simulated network in some very specific situations, the primary behaviour of a
solar system is maintained, like retrograde orbits, periodical alignment,
predictable behaviour, and recursive orbits of sub orbiting object.
